---
title: "Summer Pilot 2020"
author: "Devon Blitz, Eli Lowham, Jim Wright"
output:
  html_document:
    toc: true
    toc_float: true
    theme: spacelab
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r setup 1, include=FALSE}
library(tidyverse)
library(rio)
library(here)
library(colorblindr)
library(gghighlight)
library(forcats)
library(ggrepel)
library(gt)
library(knitr)
library(kableExtra)
library(reactable)
library(plotly)
library(SCVA)


theme_set(theme_minimal(15) +
            theme(legend.position = "bottom",
                  panel.grid.major.x = element_line(color = "gray60"),
                  panel.grid.minor.x = element_blank(),
                  panel.grid.major.y = element_blank())
          )

brief_parent <- import(here("data", "suma_brief_parent.xlsx"),
               setclass = "tbl_df") 
 
brief_self <- import(here("data", "suma_brief_self.xlsx"),
               setclass = "tbl_df") 

class_self_1 <- import(here("data", "suma_class_self_1.xlsx"),
               setclass = "tbl_df") 

class_self_2 <- import(here("data", "suma_class_self_2.xlsx"),
               setclass = "tbl_df") 

class_parent_1 <- import(here("data", "suma_class_parent_1.xlsx"),
               setclass = "tbl_df") 

class_parent_2 <- import(here("data", "suma_class_parent_2.xlsx"),
               setclass = "tbl_df") 

pcss <- import(here("data", "suma_pcss.xlsx"),
               setclass = "tbl_df") 

hit <- import(here("data", "suma_hit.xlsx"),
               setclass = "tbl_df") 

status <- import(here("data", "suma_status.xlsx"),
               setclass = "tbl_df") 

status2 <- import(here("data", "suma_status2.xlsx"),
               setclass = "tbl_df") 

gas <- import(here("data", "suma_gas.xlsx"),
               setclass = "tbl_df") 

productivity <- import(here("data", "suma_productivity.xlsx"),
               setclass = "tbl_df") 

productivity2 <- import(here("data", "suma_productivity2.xlsx"),
               setclass = "tbl_df") 

psychoeducation <- import(here("data", "suma_psychoeducation.xlsx"),
               setclass = "tbl_df") 

rm <- import(here("data", "suma_rm.xlsx"),
               setclass = "tbl_df") 
```


# Outcome Measures 

## GAS Hierarchy - Number of tasks completed per week

```{r, include=FALSE}
head(gas)

gas_tbl <- gas %>% 
  reactable(columns = list(
    Level = colDef(align = "center"),
    Outcome = colDef(align = "center")),
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE,
    height = 400,
    width = 500)
```

```{r, include=TRUE}
gas_tbl
```

## BRIEF-2 {.tabset .tabset-fade .tabset-pills}

```{r, include=FALSE}
head(brief_parent)
head(brief_self)

brief_self_tidy <- brief_self %>% 
  pivot_longer(
    cols = c(`Pre-Test`, `Post-Test`),
    names_to = "Assessment",
    values_to = "Response"
  )

head(brief_self_tidy)

brief_scales <- c("Global Executive Composite",
                  "Cognitive Regulation Index",
                  "Organization Scale",
                  "Task Completion Scale",
                  "Plan/Organize Scale",
                  "Working Memory Scale",
                  "Initiate Scale",
                  "Emotional Regulation Index",
                  "Emotional Control Scale",
                  "Shift Scale",
                  "Behavior Regulation Index",
                  "Self-Monitor Scale",
                  "Inhibit Scale")

brief_self_tidy$Assessment <- factor(brief_self_tidy$Assessment, levels = c("Pre-Test",
                                                                            "Post-Test"))

brief_self_plot <- ggplot(brief_self_tidy, aes(`Scale/Index`, `Response`)) +
  geom_line(aes(group = `Scale/Index`), color = "gray40") +
  geom_point(aes(color = `Assessment`)) +
  coord_flip() +
  scale_x_discrete(limits = brief_scales) +
  scale_y_continuous(limits = c(30, 90),
                     breaks = c(30, 35, 40, 45, 50, 55, 60, 65, 70, 75, 80, 85, 90)) +
  geom_text_repel(aes(label = `Response`)) +
  theme(plot.title = element_text(color = "black", face = "bold", hjust = 0.5),
        plot.subtitle = element_text(color = "black", face = "bold")) +
  labs(x = "",
       y = "",
       title = "BRIEF-2 Self-Report",
       subtitle = "Scores Greater than 65 are Considered Clinically Significant")

brief_self_plot


brief_parent_tidy <- brief_parent %>% 
  pivot_longer(
    cols = c(`Pre-Test`, `Post-Test`),
    names_to = "Assessment",
    values_to = "Response"
  )

brief_parent_tidy$Assessment <- factor(brief_parent_tidy$Assessment, levels = c("Pre-Test",
                                                                                "Post-Test"))

brief_parent_plot <- ggplot(brief_parent_tidy, aes(`Scale/Index`, `Response`)) +
  geom_line(aes(group = `Scale/Index`), color = "gray40") +
  geom_point(aes(color = `Assessment`)) +
  coord_flip() +
  scale_x_discrete(limits = brief_scales) +
  scale_y_continuous(limits = c(30, 90),
                     breaks = c(30, 35, 40, 45, 50, 55, 60, 65, 70, 75, 80, 85, 90)) +
  geom_text_repel(aes(label = `Response`)) +
  theme(plot.title = element_text(color = "black", face = "bold", hjust = 0.5),
        plot.subtitle = element_text(color = "black", face = "bold")) +
  labs(x = "",
       y = "",
       title = "BRIEF-2 Parent-Report",
       subtitle = "Scores Greater than 65 are Considered Clinically Significant")

brief_parent_plot
```

### BRIEF-2 Self-Report

```{r, include=TRUE, fig.height=8, fig.width=10}
brief_self_plot
```

### BRIEF-2  Parent-Report

```{r, include=TRUE, fig.height=8, fig.width=10}
brief_parent_plot
```

## CLASS {.tabset .tabset-fade .tabset-pills}

```{r, include=FALSE}
head(class_self_1)
head(class_self_2)
head(class_parent_1)
head(class_parent_2)

class_self_1_tidy <- class_self_1 %>% 
  pivot_longer(
    cols = c(`Pre-Test`, `Post-Test`),
    names_to = "Assessment",
    values_to = "Response"
  )

class_1 <- c("Easily bothered by lights/screens or noise",
             "Tiring easily during homework",
             "Tiring easily during the school day",
             "Headaches interfering with homework",
             "Headaches interfering with classwork",
             "Easily distracted during homework",
             "Easily distracted during classwork",
             "Trouble reading",
             "Trouble remembering what was studied",
             "Difficulty studying for tests or quizzes",
             "Homework taking longer",
             "In class, work taking longer",
             "Difficulty understanding new material",
             "Difficulty taking notes")

class_1_resp <- c("A lot worse",
                  "Somewhat worse",
                  "A little worse",
                  "Not worse")

class_self_1_tidy$Assessment <- factor(class_self_1_tidy$Assessment, levels = c("Pre-Test",
                                                                                "Post-Test"))

class_self_1_plot <- ggplot(class_self_1_tidy, aes(`Question`, `Response`)) +
  geom_line(aes(group = `Question`), color = "gray40") +
  geom_point(aes(color = `Assessment`)) +
  coord_flip() +
  scale_x_discrete(limits = class_1) +
  scale_y_discrete(limits = class_1_resp) +
  theme(plot.title = element_text(color = "black", face = "bold", hjust = 0.5),
        plot.subtitle = element_text(color = "black", face = "bold")) +
  labs(x = "",
       y = "",
       title = "CLASS Responses",
       subtitle = "Questions 1-14")

class_self_1_plot

class_self_2_tidy <- class_self_2 %>% 
  pivot_longer(
    cols = c(`Pre-Test`, `Post-Test`),
    names_to = "Assessment",
    values_to = "Response"
  )

class_2 <- c("Stressed out about your grades dropping",
             "More stressed out/overwhelmed with the schoolwork piling up",
             "Not having enough support at home from parents/siblings",
             "Not having enough support from teachers",
             "Not being allowed to play sports/recreation",
             "Missing time with friends and/or social activities")

class_2_resp <- c("Very stressful",
                  "Moderately stressful",
                  "A little stressful",
                  "Not stressful")

class_self_2_tidy$Assessment <- factor(class_self_2_tidy$Assessment, levels = c("Pre-Test",
                                                                                "Post-Test"))

class_self_2_plot <- ggplot(class_self_2_tidy, aes(`Question`, `Response`)) +
  geom_line(aes(group = `Question`), color = "gray40") +
  geom_point(aes(color = `Assessment`)) +
  coord_flip() +
  scale_x_discrete(limits = class_2) +
  scale_y_discrete(limits = class_2_resp) +
  theme(plot.title = element_text(color = "black", face = "bold", hjust = 0.5),
        plot.subtitle = element_text(color = "black", face = "bold")) +
  labs(x = "",
       y = "",
       title = "CLASS Responses",
       subtitle = "Questions 15-20")

class_self_2_plot

class_parent_1_tidy <- class_parent_1 %>% 
  pivot_longer(
    cols = c(`Pre-Test`, `Post-Test`),
    names_to = "Assessment",
    values_to = "Response"
  )


class_parent_1_tidy$Assessment <- factor(class_parent_1_tidy$Assessment, levels = c("Pre-Test",
                                                                                    "Post-Test"))

class_parent_1_plot <- ggplot(class_parent_1_tidy, aes(`Question`, `Response`)) +
  geom_line(aes(group = `Question`), color = "gray40") +
  geom_point(aes(color = `Assessment`)) +
  coord_flip() +
  scale_x_discrete(limits = class_1) +
  scale_y_discrete(limits = class_1_resp) +
  theme(plot.title = element_text(color = "black", face = "bold", hjust = 0.5),
        plot.subtitle = element_text(color = "black", face = "bold")) +
  labs(x = "",
       y = "",
       title = "CLASS Responses",
       subtitle = "Questions 1-14")

class_parent_1_plot

class_parent_2_tidy <- class_parent_2 %>% 
  pivot_longer(
    cols = c(`Pre-Test`, `Post-Test`),
    names_to = "Assessment",
    values_to = "Response"
  )

class_parent_2_tidy$Assessment <- factor(class_parent_2_tidy$Assessment, levels = c("Pre-Test",
                                                                                    "Post-Test"))

class_parent_2_plot <- ggplot(class_parent_2_tidy, aes(`Question`, `Response`)) +
  geom_line(aes(group = `Question`), color = "gray40") +
  geom_point(aes(color = `Assessment`)) +
  coord_flip() +
  scale_x_discrete(limits = class_2) +
  scale_y_discrete(limits = class_2_resp) +
  theme(plot.title = element_text(color = "black", face = "bold", hjust = 0.5),
        plot.subtitle = element_text(color = "black", face = "bold")) +
  labs(x = "",
       y = "",
    title = "CLASS Responses",
       subtitle = "Questions 15-20")

class_parent_2_plot
```

### CLASS Self 1

```{r, include=TRUE, fig.height=8, fig.width=10}
class_self_1_plot
```

### CLASS Self 2

```{r, include=TRUE, fig.height=8, fig.width=11}
class_self_2_plot
```

### CLASS Parent 1

```{r, include=TRUE, fig.height=8, fig.width=10}
class_parent_1_plot
```

### CLASS parent 2

```{r, include=TRUE, fig.height=8, fig.width=11}
class_parent_2_plot
```

## PCSS

```{r, include=FALSE}
head(pcss)

pcss_table <- pcss %>% 
  reactable(
    columns = list(
      `Pre Test` = colDef(name = "Pre-Test"),
      `Post Test` = colDef(name = "Post-Test")),
    pagination = FALSE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE,
    searchable = TRUE,
    height = 600,
    width = 500)
```

```{r pcss table, include=TRUE, fig.height=8}
pcss_table
```

## HIT

```{r, include=FALSE}
head(hit)

hit_positions <- c("Pre-Test", "Post-Test")

hit_plot <- ggplot(hit, aes(measure, score)) +
  geom_hline(yintercept = 50, 
             linetype = "dashed",
             size = 1) +
  geom_col(fill = "blue", 
           alpha = 0.7) +
  scale_x_discrete(limits = hit_positions) +
  scale_y_continuous(limits = c(0, 60),
                     breaks = c(10, 20, 30, 40, 50, 60)) + 
  geom_text(aes(measure, score, label = score),
            nudge_y = -3,
            color = "white") +
  theme(plot.title = element_text(color = "black", face = "bold", hjust = 0.5)) +
  labs(x = "",
       y = "Score",
       title = "HIT Results",
       caption = "Score of 50 or Greater Suggest Headaches Impact Daily Functioning") 

hit_plot
```

```{r hit plot, include=TRUE, fig.height=8, fig.width=8}
hit_plot
```


# Repeated Measures 

## Status {.tabset .tabset-fade .tabset-pills}

```{r, include=FALSE}
head(status)

#graph(design = "AB", 
     # data = status,
     # xlab = "Session Number",
      #ylab = "Weekly Tasks Completed",
      #ylim = c(0, 10),
      #labels = NULL)

status_plot <- ggplot(status, aes(session, status)) +
  geom_line() +
  geom_point(size = 2) +
  scale_x_continuous(limits = c(0, 6),
                     breaks = c(1, 2, 3, 4, 5, 6)) +
  scale_y_continuous(limits = c(0, 12),
                     breaks = c(0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12)) +
  theme_classic() +
  theme(plot.title = element_text(color = "black", face = "bold", hjust = 0.5)) +
  labs(x = "Session",
       y = "Weekly Tasks Completed",
       title = "Status Tracking Goal") 

head(status2)

status_plot2 <- ggplot() +
  geom_line(data = status2, aes(x = session, y = bl)) +
  geom_point(data = status2, aes(x = session, y = bl), size = 2) +
  geom_line(data = status2, aes(x = session, y = tx)) +
  geom_point(data = status2, aes(x = session, y = tx), size = 2) +
  scale_x_continuous(limits = c(0, 6),
                     breaks = c(1, 2, 3, 4, 5, 6)) +
  scale_y_continuous(limits = c(0, 12),
                     breaks = c(0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12)) +
  theme_classic() +
  theme(plot.title = element_text(color = "black", face = "bold", hjust = 0.5)) +
  labs(x = "Session",
       y = "Weekly Tasks Completed",
       title = "Status Tracking Goal") 

status_plot2

head(productivity)

productivity_plot <- ggplot(productivity, aes(session, product)) +
  geom_line() +
  geom_point(size = 2) +
  scale_x_continuous(limits = c(0, 6),
                     breaks = c(1, 2, 3, 4, 5, 6)) +
  scale_y_continuous(limits = c(0, 5),
                     breaks = c(0, 1, 2, 3, 4, 5)) +
  theme_classic() +
  theme(plot.title = element_text(color = "black", face = "bold", hjust = 0.5)) +
  labs(x = "Session",
       y = "Level of Perception",
       title = "Perception of Weekly Productivity",
       caption = "1 = completed none of the tasks I wanted to\n 2 = completed not enough of the tasks I wanted to\n 3 = completed some of the tasks I wanted to\n 4 = completed most but not all of the tasks I wanted to\n 5 = completed all of the tasks I wanted to") 


head(productivity2)

productivity_plot2 <- ggplot() +
  geom_line(data = productivity2, aes(x = session, y = bl)) +
  geom_point(data = productivity2, aes(x = session, y = bl), size = 2) +
  geom_line(data = productivity2, aes(x = session, y = tx)) +
  geom_point(data = productivity2, aes(x = session, y = tx), size = 2) +
  scale_x_continuous(limits = c(0, 6),
                     breaks = c(1, 2, 3, 4, 5, 6)) +
  scale_y_continuous(limits = c(0, 5),
                     breaks = c(0, 1, 2, 3, 4, 5)) +
  theme_classic() +
  theme(plot.title = element_text(color = "black", face = "bold", hjust = 0.5)) +
  labs(x = "Session",
       y = "Level of Perception",
       title = "Perception of Weekly Productivity",
       caption = "1 = completed none of the tasks I wanted to\n 2 = completed not enough of the tasks I wanted to\n 3 = completed some of the tasks I wanted to\n 4 = completed most but not all of the tasks I wanted to\n 5 = completed all of the tasks I wanted to") 

productivity_plot2
```

### Status Plot 1

```{r, include=TRUE}
status_plot
```

### Status Plot 2

```{r, include=TRUE}
status_plot2
```

### Productivity Perception Plot

```{r, include=TRUE}
productivity_plot
```

### Productivity Perception Plot 2

```{r, include=TRUE}
productivity_plot2
```

## Psychoeducation Plot

```{r, include=FALSE}
head(psychoeducation)

psychoeducation_plot <- ggplot(psychoeducation, aes(session, pe)) +
  geom_line() +
  geom_point(size = 2) +
  scale_x_continuous(limits = c(1, 3),
                     breaks = c(1, 2, 3)) +
  scale_y_continuous(limits = c(0, 5),
                     breaks = c(1, 2, 3, 4, 5)) +
  theme_classic() +
  theme(plot.title = element_text(color = "black", face = "bold", hjust = 0.5)) +
  labs(x = "Session",
       y = "Level of Agreement",
       title = "Participant Agreement on Ability\n to Teach Back Delivered Psychoeducation",
       caption = "1 = Strongly disagree\n 2 = Disagree\n 3 = Neutral\n 4 = Agree\n 5 = Strongly agree") 

psychoeducation_plot

```

```{r psychoeducation plot, include=TRUE}
psychoeducation_plot
```

## Frequency of Strategy Use
```{r frequency, include=FALSE}
head(rm)

suma_freq <- rm %>% 
  select(session, frequency)

suma_freq_plot <- ggplot(suma_freq, aes(session, frequency)) +
  geom_line() +
  geom_point(size = 2) +
  scale_x_continuous(limits = c(4, 6),
                     breaks = c(4, 5, 6)) +
  scale_y_continuous(limits = c(0, 20),
                     breaks = c(0, 2, 4, 6, 8, 10, 12, 14, 16, 18, 20)) +
  theme_classic() +
  theme(plot.title = element_text(color = "black", face = "bold", hjust = 0.5)) +
  labs(x = "Session",
       y = "Number of Tasks",
       title = "Weekly Number of Tasks Entered into Planner") 
  
suma_freq_plot

```

```{r frequency plot, include=TRUE}
suma_freq_plot
```

## Perceived Strategy Helpfulness 

```{r helpfulness, include=FALSE}
suma_help <- rm %>% 
  select(session, help)

suma_help_plot <- ggplot(suma_help, aes(session, help)) +
  geom_line() +
  geom_point(size = 2) +
  scale_x_continuous(limits = c(4, 6),
                     breaks = c(4, 5, 6)) +
  scale_y_continuous(limits = c(0, 5),
                     breaks = c(1, 2, 3, 4, 5)) +
  theme_classic() +
  theme(plot.title = element_text(color = "black", face = "bold", hjust = 0.5)) +
  labs(x = "Session",
       y = "Level of Helpfulness",
       title = "Perceived Helpfulness of Planner",
       caption = "1 = Not Helpful at All\n 2 = Not Helpful\n 3 = Somewhat Helpful\n 4 = Helpful\n 5 = Very Helpful") 

suma_help_plot
  
```

```{r helpfulness plot, include=TRUE}
suma_help_plot
```